A Linked Open Social Dataset for Scientific Benchmarking

### 2019-06-20 tables/nsnapshots.tex
adiantado um pouco do artigo

\begin{table*}[h!]
\begin{center}
\caption{Number of snapshots from each provenance.}
\begin{tabular}{| l | c |}\hline
\textbf{social protocol} & \textbf{number of snapshots} \\\hline\hline
Algorithmic Autoregulation & 3 \\\hline
Cidade Democrática & 1 \\\hline
Email & 4 \\\hline
Facebook & 88 \\\hline
IRC & 4 \\\hline
ParticipaBR & 1 \\\hline
Twitter & 16 \\\hline\hline
all & 117 \\\hline
\end{tabular}\end{center}
\end{table*}

>>>>

\begin{table*}[h!]
\begin{center}
\caption{Number of snapshots from each provenance.}
\begin{tabular}{ l | c }
\textbf{social protocol} & \textbf{number of snapshots} \\\hline
Algorithmic Autoregulation & 3 \\
Cidade Democrática & 1 \\
Email & 4 \\
Facebook & 88 \\
IRC & 4 \\
ParticipaBR & 1 \\
Twitter & 16 \\\hline
all & 117 \\
\end{tabular}\end{center}
\end{table*}
